Mixed language processing increases cross-language phonetic transfer in Bengali-English Bilinguals

### 2021-05-24 draft_glossa-psych/glossa-psych_AM-ID_manuscript.tex
figure legends, glosses

\usepackage{tabularx}

@@

\author[Auromita \& Indranil]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{Auromita Mitra\\ 
  \institute{The EFL University}\\
  \small{%105, Bd. Raspail, 75005 Paris\\
  auromita.mitra@gmail.com}
  }
  \AND
  \spauthor{Indranil Dutta \\
  \institute{Jadavpur University}\\
  \small{%Warmoesberg 26, 1000 Brussel\\
  indranildutta.lnl@jadavpuruniversity.in}
  }%
}
\begin{document}

@@

	\item Code-switching: Each slide contained one target word embedded in either an English (unilingual) or a Bengali (mixed; target produced as a switch from Bengali) carrier sentence which was read out by the participant. The carrier sentences are given below:
	\begin{itemize}
		\item Unilingual sentence: That is a yellow [Target Word].
		\item Mixed-language sentence: \textipa{o-ta \ae k-ta ka:lo} [Target Word].
	\end{itemize}

>>>>

@@

\author[Auromita \& Indranil]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{Auromita Mitra\\ 
  \institute{The EFL University}\\
  \small{%105, Bd. Raspail, 75005 Paris\\
  auromita.mitra@gmail.com}
  }
  \AND
  \spauthor{Indranil Dutta \\
  \institute{Jadavpur University}\\
  \small{%Warmoesberg 26, 1000 Brussel\\
  indranildutta.lnl@jadavpuruniversity.in}
  }%
}
%\usepackage{gb4e}
\begin{document}

@@

	\item Code-switching: Each slide contained one target word embedded in either an English (unilingual) or a Bengali (mixed; target produced as a switch from Bengali) carrier sentence which was read out by the participant. The carrier sentences are given below:
	\begin{itemize}
		\item Unilingual sentence: That is a yellow [Target Word].
		\item Mixed-language sentence: \textipa{o-\:ta \ae k-\:ta kalo} [Target Word]. 
	\end{itemize}

Gloss and translation for Bengali sentence:

	o-ta \quad Ek-ta \quad kalo [target word]\\
	that-CL one-CL black [target word]\\
	that is a black [target word]\\
